Co-moving stars in \textsl{Gaia DR1}: a catalog of genuine comoving star pairs from low-resolution spectroscopic follow-up

### 2017-06-03 paper/comoving-followup.tex
starting to write words about sky line fixes

This wavelength calibration procedure produces a nightly model for the
nonlinear dispersion of wavelength as a function of pixel value for each
extracted 1D spectrum.
However, because of flexure in the spectrograph, each observation will have an
additional offset of, typically, $\approx 0.5$--$2~{\rm \AA}$, corresponding to
a significant velocity offset at ${\rm H}\alpha$ of $\approx 20$--$100~\kms$.
\figurename~\ref{fig:sample-spectra} shows a random sample of 10 source spectra
of comoving star pair members normalized to 1 at $\lambda = 5500~{\rm \AA}$ and
shifted by index for visualization.
From the appearances of these 10 spectra, it seems there is a mix of
metallicities and spectral types amongst the observed targets.
Note that the spectra are not flux-calibrated, as we only care about measuring
radial velocities from this sample.

@@

>>>>

This wavelength calibration procedure produces a nightly model for the
nonlinear dispersion of wavelength as a function of pixel value for each
extracted 1D spectrum.
However, because of flexure in the spectrograph, each observation will have an
additional offset of, typically, $\approx 0.5$--$2~{\rm \AA}$, corresponding to
a significant velocity offset at ${\rm H}\alpha$ of $\approx 25$--$100~\kms$.
\figurename~\ref{fig:sample-spectra} shows a random sample of 10
wavelength-calibrated source spectra of comoving star pair members normalized
to 1 at $\lambda = 5500~{\rm \AA}$ and shifted by index for visualization.
Suggested by the features in these 10 spectra, there is a mix of metallicities
and spectral types amongst the observed targets.
Note that the spectra are not flux-calibrated, as we only care about measuring
radial velocities from this sample.

@@

As mentioned previously, comparison lamp spectra were not obtained at each
telescope pointing.
Depending primarily on the hour angle of the observation (because of the orientation of the spectrograph and CCD), there
